---
title: "Titanic Data"
author: "Ramon Mata"
params:
  date: !r date()  
  rversion: !r getRversion()  
  rsversion: "1.0.143"  
output:
  github_document: default
  html_notebook: default
---

This notebook contains the exploratory analysis and modeling for the *Titanic Getting Started Prediction Competition*, it also tries to document some of hte *R* commands executed

<small>
**R Version**: `r params$rversion` <br>
**RStudio Version**: `r params$rsversion` <br>
**Last update**: `r params$date`
</small>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning = FALSE, comment = FALSE)
```

## Load Packages and Data Files
The following commands add the specified variables to the R environment so we can use their functionality
```{r}
# Data Visualisation and themes
library('ggplot2')
library('ggthemes')

# Scale functions for Visualisations
library('scales')

# Data Manipulation
suppressMessages(library('dplyr'))

# Classification and Regression with Random Forest
suppressMessages(library('randomForest'))

```
The supressMessage function will *"suppress"* the extra information printed by the later 2 packages.

Write `?supressMessages` in the *R* console to get more information

## Loading Data
```{r}
# Load train and test files provided by Kaggle and
# not reading string as Factors
train <- read.csv('data/train.csv', stringsAsFactors = FALSE)
test <- read.csv('data/test.csv', stringsAsFactors = FALSE)
```

- See [Factors](https://stat.ethz.ch/R-manual/R-devel/library/base/html/factor.html)
- or type `?factor` within *R* console for help

After Data is loaded in *R* Global Environment, we can take a quick look at the data by executing the following:
```{r}
str(train)
str(test)
```

After execution of `str()` for both data files, we can see some information about the files like:

- Train file has more observations
- An extra variable `Survived` exists in train file
- Age may contain: `NA`
- Cabin may come as empty string: ""

## Exploratory Analysis - <small>*As is*</small>

### Age <small>vs</small> Survived
```{r  message=F, warning=F}
ggplot(train, aes(Age, fill = factor(Survived, labels = c("No","Yes")))) +
  geom_histogram(bins = 30) +
  theme_minimal() +
  xlab("Age") +
  ylab("Count") +
  scale_fill_discrete(name = "Survived")
```

### Sex <small>vs</small> Survived
```{r}
ggplot(train, aes(Sex, fill = factor(Survived, labels = c("No","Yes")))) +
  geom_bar(stat = "count") +
  theme_minimal() +
  xlab("Sex") +
  ylab("Count") +
  scale_fill_discrete(name = "Survived")
```

### Age <small>vs</small> Sex <small>vs</small> Survived
```{r message=F, warning=F}

ggplot(train, aes(Age, fill = factor(Survived, labels = c("No","Yes")))) +
  geom_histogram(bins = 30) +
  theme_minimal() +
  xlab("Age") +
  ylab("Count") +
  facet_grid(.~Sex)+
  scale_fill_discrete(name = "Survived")
```

### Class <small>vs</small> Sex <small>vs</small> Survived
```{r}
#scale_fill_brewer(palette="Greys", name = "Survived")
ggplot(train, aes(Pclass, fill = factor(Survived, labels = c("No","Yes")))) +
  geom_bar(stat = "count") +
  theme_minimal() +
  facet_grid(~Sex)+
  xlab("Passenger Class") +
  ylab("Count") +
  scale_fill_discrete(name = "Survived")
```

### Class <small>vs</small> Sex <small>vs</small> Age <small>vs</small> Survived
```{r}
ggplot(train, aes(x = Age, y = Sex)) +
  geom_jitter(aes(colour = factor(Survived, labels = c("No","Yes")))) +
  theme_minimal() +
  facet_wrap(~Pclass) +
  labs(x = "Age", y = "Sex", colour = "Survived") +
  scale_x_continuous(name="Age",limits=c(0, 81))

```


## Data Processing and Exploratory Analysis

## Modeling with Random Forest

## Cross - Validation ?

## Prediction

