---
title: "Titanic Data"
author: "Ramon Mata"
output:
  github_document
params:
  date: !r date()
  rversion: !r getRversion()
---

This notebook contains the exploratory analysis and modeling for the *Titanic Getting Started Prediction Competition*, it also tries to document **R** commands executed

*Update Date: `r params$date`*  <br>
*R version: `r params$rversion`*  

## Packages and Data Files
The following commands add the specified variables to the R environment so we can use their functionality
```{r}
# Data Visualisation and themes
library('ggplot2')
library('ggthemes')

# Scale functions for Visualisations
library('scales')

# Data Manipulation
suppressMessages(library('dplyr'))

# Classification and Regression with Random Forest
suppressMessages(library('randomForest'))

```
The supressMessage function will *"suppress"* the extra information printed by the later 2 packages.

Write `?supressMessages` in the R console to get help

## Loading Data
```{r}
# Load train and test files provided by Kaggle and
# not reading string as Factors
train <- read.csv('data/train.csv', stringsAsFactors = FALSE)
test <- read.csv('data/test.csv', stringsAsFactors = FALSE)
```

- See [Factors](https://stat.ethz.ch/R-manual/R-devel/library/base/html/factor.html)
- `?factor` in the R console for help

After Data is loaded in R Global Environment, we can take a quick look at the data by executing the following:
```{r}
str(train)
str(test)
```

Thigs we notice after the execution of `str()` for both data files

- We have an extra variable `Survived` in train file
- Age contains `NA`
- Cabin may come as empty string
?@|@

## Exploratory Analysis

### Age vs Survived
```{r}
ggplot(train, aes(Age, fill = factor(Survived))) +
  geom_histogram(bins=30) +
  theme_minimal() +
  xlab("Age") +
  scale_fill_discrete(name = "Survived")
```
### Sex vs Survived
```{r}
ggplot(train, aes(Sex, fill = factor(Survived))) +
  geom_histogram(stat = "count") +
  theme_minimal() +
  xlab("Sex") +
  scale_fill_discrete(name = "Survived")
```

### Age vs Sex vs Survived
```{r}
ggplot(train, aes(Age, fill = factor(Survived))) +
  geom_histogram(bins=30) +
  theme_minimal() +
  xlab("Age") +
  ylab("Count") +
  facet_grid(.~Sex)+
  scale_fill_discrete(name = "Survived")
```

## Data Processing and Exploratory Analysis

## Modeling with Random Forest

## Cross - Validation ?

## Prediction

